\documentclass[a4paper,12pt]{report}
\usepackage[tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in]{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{PTSans}
\usepackage{droidserif}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}

% Set sans serif font to PT Sans
%\setsansfont{\usefont{T1}{PTSans-TLF}{b}{n}PT Sans Bol}
% Set serifed font to Droid Serif
%\setmainfont{Droid Serif}
% Set formats for each heading level
\titleformat*{\section}{\fontsize{16}{18}\bfseries\sffamily}
\titleformat*{\subsection}{\fontsize{14}{16}\bfseries\sffamily}
\titleformat*{\subsubsection}{\fontsize{12}{14}\bfseries\sffamily}
\begin{document}

\title{Phoenix Documentation}

\include{title}
 
\chapter{Introduction}
Phoenix is a distributed agent-based simulation platform designed for
development of agent-based systems and simulations. We use agent based
models and simulations in our study of complex systems,
micro-simulations and bottom-up approaches to engineering.

This document explains the motivations, design, architecture of the
new agent based simulation framework. It will also explain the
motivations behind some of the design decisions so that we provide the
right hooks for people looking to extend or modify the platform for
themselves. 

The platform is released with both the source code and the design
documents as well as adequate explanations.

This documentation will also guide users to develop simple agent-based
models and also include some case-studies of some models as well as
possible ideas for extension of the platform.

\chapter{Motivation}
In this section we discuss the motivation to create a new agent based
 platform.
\section{Modelling Complex Systems}
There are many approaches to modelling complex systems. We would like
to classify them broadly into predictive models and generative
models. (The generative models are similar to the approach to
modelling as described by Epstine et.al in there book, generative
social science.) The nature of complex systems do not allow for
building of predictive models. Complex systems interact in intractable
ways which are not easily succeptable to data observations. Thus, a
lot of data and observations will not be avaliable to build and
compare the built models.

\subsection{An example to expalin complex system behaviour}

Let us take a simple thought experiment to imagine complex
systems. Imagine looking at a film-reel. A film reel is a series of
photographs that are taken one after another forming a series of
photographs. Each photograph forms a frame. By playing the reel at 30
frames per second gives us the illusion of moving picture, a movie
(due to persistence of vision).

Linear systems are like a film reel. By following the frames on the
reel one can deduce the story that the pictures are saying. In case a
frame or a set of frames are missing in between them you can always
see the frames at the extremities and \textit{draw} new frames or
deduce to a good extent, what the pictures in the missing frames would
look like. This is because the film real follows a linear causality,
i.e. it is ensured that after one frame with one picture, the next
frame will hold the next logical frame. Given this guarantee one can
go back in the reel to deduce lost pictures. One can also draw new
pictures, at the end of a reel. We will also be able to tell where a
scene began by tracing our steps back to the using the frames as the
frames remain static. Thus, a linear, static, tractable system.

Now imagine instead of a single strip of film you are given a fabric
of such photograph frames (as if on a checker pattern blanket where
each box has a frame). To begin with how would one start reading such
a piece? There is no definite start or end as any part of such a
blanket can become the start or the end. There is another
complication; imagine if the pictures do not have a causal relation
ship, i.e. the adjacent pictures have nothing in common. There is no
define way to establish a story. Given a starting point we have no
idea as to which picture to jump next. This complicates the matter
immensely as one cannot justify where the movie would start or
end. One also fails to fill missing frames as we do not know how the
frames are related. If a person starts filling frames randomly, there
is no way for us to say if the scene is correct or, to make it worse,
how did the scene even come about in the first place. In this blanket
example, there are only two dimensions of frames, but, what if there
were more dimensions? Thus, the system becomes intractable and
non-linear. To add to our woes if the frames also kept shifting their
places then the system becomes dynamic too!


Another reason for non-avaliability of data is that most complex
system components are themselves areas of active research. For example
behavioural economics still conducts experiments on how a community
considers utility of various resources at its disposal.

However, one can still study complex systems using generative
models. The objective of such models is in their ability in explaining
the behaviour of the system i.e. it can explain the trajectory of
certain outcomes of the complex system. This infomration can be used
to understand or look for failure (or unwanted) states and thus test
designs for such complex systems.
\section{Complex Systems and Agent-Based Models}
\section{Other approaches to studying complex systems}
\subsection{Systems Dynamics}
\subsection{Complex Networks}

\chapter{Design and Architecture of Phoenix}
\include{design}

\chapter{Implementation of Phoenix}
\include{implementation}

\chapter{Extending Phoenix and Module Architecture}
\section{Current Modules}
\section{Future Modules}

\chapter{Using Phoenix}
\section{Basic Configuration}
\section{High Avaliability Configuration}

\chapter{Performance of Phoenix}

\chapter{Example Models using Phoenix}

\end{document}
